Openness and Computational Reproducibility in plant pathology: where do we stand and a way forward

### 2022-05-20 analysis/paper/paper.Rmd
add a missing "," after e.g.

```{r articleScores, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Aggregated article scores for each of the four categories, (A) shows computational methods availability 0 - not available or not mentioned to 3 - freely available online to anonymous users. (B) presents 'Software availability', where '0' was 'Not available or not mentioned in the publication'; '1' was 'Expensive proprietary software that only institutions would typically purchase'; '2' was 'Used proprietary software that most individuals can afford (e.g., Excel) or SAS that is now available free for use with a university login'; and '3' was 'Used entirely open source and free software (e.g., R, Julia, Python)'; 'NA' indicates that no specialised software was necessary or used. (C) displays 'Software citated', where '0' was 'Not available or not mentioned in the publication'; '1' was 'Software mentioned by name only'; '2' was 'Software cited with version number'; and '3' was 'All software components (SAS PROCs, R, Julia or Python packages, etc.) cited'; 'NA' indicates that no specialised software was necessary or used. (D) shows 'Data availability', where '0' was 'Not available or not mentioned in the publication'; '1' was 'Available upon request to the author; '2' was 'Online, but inconvenient or non-permanent (e.g., login needed, paywall, FTP server, personal lab website that may disappear, or may have already disappeared)'; and '3' was 'Freely available online to anonymous users for foreseeable future (e.g., archived using Zenodo, dataverse or university library or some other proper archiving system)'; 'NA' indicates that no data were generated, e.g. a methods paper.", cache=FALSE, fig.env='figure'}

>>>>

```{r articleScores, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Aggregated article scores for each of the four categories, (A) shows computational methods availability 0 - not available or not mentioned to 3 - freely available online to anonymous users. (B) presents 'Software availability', where '0' was 'Not available or not mentioned in the publication'; '1' was 'Expensive proprietary software that only institutions would typically purchase'; '2' was 'Used proprietary software that most individuals can afford (e.g., Excel) or SAS that is now available free for use with a university login'; and '3' was 'Used entirely open source and free software (e.g., R, Julia, Python)'; 'NA' indicates that no specialised software was necessary or used. (C) displays 'Software citated', where '0' was 'Not available or not mentioned in the publication'; '1' was 'Software mentioned by name only'; '2' was 'Software cited with version number'; and '3' was 'All software components (SAS PROCs, R, Julia or Python packages, etc.) cited'; 'NA' indicates that no specialised software was necessary or used. (D) shows 'Data availability', where '0' was 'Not available or not mentioned in the publication'; '1' was 'Available upon request to the author; '2' was 'Online, but inconvenient or non-permanent (e.g., login needed, paywall, FTP server, personal lab website that may disappear, or may have already disappeared)'; and '3' was 'Freely available online to anonymous users for foreseeable future (e.g., archived using Zenodo, dataverse or university library or some other proper archiving system)'; 'NA' indicates that no data were generated, e.g., a methods paper.", cache=FALSE, fig.env='figure'}
